---
title: "group_12_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group_12_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CD12)
```

Package description:

The current package consists of 7 functions. 




Function 1:

This function carries out the random DNA sequence generation of a specified length.
It takes one argument, "seq_length", which needs to be a positive integer, representing the wanted length of the sequence to be created. 
As an output, it gives the string "seq_str", which is the resulting sequence. 
This function is tested based on 2 parameters:
1. The length of the output sequence (the number of characters of the output string) must be equal to the given argument
2. The output string should only include the characters A, T, G, or C.


Function 2:

Function 3:

Function 4:

Function 5:






Use Cases and Additional Functions:





